`inferCNV` results exploration for `r params$sample_id`

### 2025-12-17 analyses/cell-type-ewings/template_notebooks/cnv-workflow/01-marker-genes.Rmd
manually run typos to fix a bunch of typos that are reasonable to fix

```{r, fig.height=10, fig.width=10, eval=has_marker_gene_exp}
marker_plot_df <- celltype_df |>
  dplyr::mutate(gene_expresed = dplyr::if_else(transformed_gene_expression > 0, TRUE, FALSE)) |>
  dplyr::select(gene_symbol, gene_expresed, sum_classification)

ggplot(marker_plot_df, aes(x = sum_classification, fill = gene_expresed)) +
  geom_bar(stat = "count") +
  facet_grid(rows = vars(gene_symbol)) +
  scale_fill_manual(values = c("grey", "blue")) +
  theme_classic()
```

>>>>

```{r, fig.height=10, fig.width=10, eval=has_marker_gene_exp}
marker_plot_df <- celltype_df |>
  dplyr::mutate(gene_expressed = dplyr::if_else(transformed_gene_expression > 0, TRUE, FALSE)) |>
  dplyr::select(gene_symbol, gene_expressed, sum_classification)

ggplot(marker_plot_df, aes(x = sum_classification, fill = gene_expressed)) +
  geom_bar(stat = "count") +
  facet_grid(rows = vars(gene_symbol)) +
  scale_fill_manual(values = c("grey", "blue")) +
  theme_classic()
```

### 2025-12-17 analyses/cell-type-wilms-tumor-06/notebook_template/03_clustering_exploration.Rmd
manually run typos to fix a bunch of typos that are reasonable to fix

---
title: "Clustering exploration for `r params$sample_id`"
author: "Maud PLASCHKA"
date: '2024-08-13'
params:
  scpca_project_id: "SCPCP000006"
  sample_id: "SCPCS000176"
  seed: 12345
  padj_thershold: 0.05  # Threshold for adjusted p-value
  lfc_threshold: 1      # Threshold for log fold change
  rate1_threshold: 0.5  # Threshold for rate (percentage) of cells expressing the marker genes in group1
  testing: 0            # When testing, certain parameter values have to be changed, and certain chunks are skipped
output:
  html_document:
    toc: yes
    toc_float: yes
    code_folding: hide
    highlight: pygments
    df_print: paged
---

@@

```{r fig.width=10, fig.height=10, out.width='100%', eval=!params$testing}
# this chunk is not run in testing (CI) since there are generally too few clusters for the method to work
feature_conversion <- srat@assays$RNA@meta.data
de_results <- DElegate::FindAllMarkers2(srat, group_column = "seurat_clusters")
# filter the most relevant markers
s.markers <- de_results[de_results$padj < params$padj_thershold & de_results$log_fc > params$lfc_threshold & de_results$rate1 > params$rate1_threshold, ]
# add gene symbol for easiest interpretation of the result
s.markers$gene_ids <- s.markers$feature
s.markers <- left_join(s.markers, feature_conversion, by = c("gene_ids"))
stopifnot(
  "Error joining gene ids and feature names" = identical(s.markers$feature, s.markers$gene_ids)
)
```

>>>>

---
title: "Clustering exploration for `r params$sample_id`"
author: "Maud PLASCHKA"
date: '2024-08-13'
params:
  scpca_project_id: "SCPCP000006"
  sample_id: "SCPCS000176"
  seed: 12345
  padj_threshold: 0.05  # Threshold for adjusted p-value
  lfc_threshold: 1      # Threshold for log fold change
  rate1_threshold: 0.5  # Threshold for rate (percentage) of cells expressing the marker genes in group1
  testing: 0            # When testing, certain parameter values have to be changed, and certain chunks are skipped
output:
  html_document:
    toc: yes
    toc_float: yes
    code_folding: hide
    highlight: pygments
    df_print: paged
---

@@

```{r fig.width=10, fig.height=10, out.width='100%', eval=!params$testing}
# this chunk is not run in testing (CI) since there are generally too few clusters for the method to work
feature_conversion <- srat@assays$RNA@meta.data
de_results <- DElegate::FindAllMarkers2(srat, group_column = "seurat_clusters")
# filter the most relevant markers
s.markers <- de_results[de_results$padj < params$padj_threshold & de_results$log_fc > params$lfc_threshold & de_results$rate1 > params$rate1_threshold, ]
# add gene symbol for easiest interpretation of the result
s.markers$gene_ids <- s.markers$feature
s.markers <- left_join(s.markers, feature_conversion, by = c("gene_ids"))
stopifnot(
  "Error joining gene ids and feature names" = identical(s.markers$feature, s.markers$gene_ids)
)
```

### 2025-12-17 analyses/cell-type-wilms-tumor-06/supplemental_notebooks/cnv_exploration/06_infercnv_exploration.Rmd
manually run typos to fix a bunch of typos that are reasonable to fix

```{r}
Do_CNV_score <- function(seurat_oject, infercnv_obj, reference_value) {
  score <- apply(infercnv_obj@expr.data, 2, function(x) {
    sum(x < 0.95 | x > 1.05) / length(x)
  })

  seurat_obj <- AddMetaData(seurat_oject, score, col.name = glue::glue("CNV-score_", reference_value))
  return(seurat_obj)
}
```

>>>>

```{r}
Do_CNV_score <- function(seurat_object, infercnv_obj, reference_value) {
  score <- apply(infercnv_obj@expr.data, 2, function(x) {
    sum(x < 0.95 | x > 1.05) / length(x)
  })

  seurat_obj <- AddMetaData(seurat_object, score, col.name = glue::glue("CNV-score_", reference_value))
  return(seurat_obj)
}
```
